---
title: "Exploratory Cannabis Analysis"
output: html_notebook
---

# Should I Smoke This? 

_an exploratory darknet market cannabis analysis_

Over the years much has been made of so-called darknet markets - anonymous forums for commerce that exist largely on the Tor network. This analysis seeks to predict quality of cannabis from market listings, based on 

- product descriptions
- price
- derived textual variables from product and feedback fields
- a set of ordinal feedback scores provided
- where it's from
- what day of the month it is
- a vendor's number of listings

A first major assumption: all of this is true.


```{r load data}
# load data -------------------------------------------------------------------

library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)

cannabis <- fread("data/cannabis-V1.csv", stringsAsFactors = T)
cannabis <- as.data.frame(cannabis)

```

The Cannabis dataset is subsetted from a larger dataset of daily darknet market listings. The market itself was Agora, the data from Black Market Archives. It covers approximately 18 months of daily listings; another feature of note is that it was, for a time, the largest darknet market in operation following the demise of Silk Road 2. 

```{r}

# feedback distribution
summary(cannabis$fb)
```

Here we have feedback scores ranging on a scale from 0 to 5 (5/5 being the best; 0/5 being the worst). The `-1` assigned here refers to listings that had _no feedback_; these are of note because they generally indicate that the product listed went unsold, for any number of reasons (but generally trust, poor price/quality). The culture of the darknet encouraged buyers to leave feedback on transactions; unlike clearnet ecommerce, feedback weighs more heavily on the darknet due to their anonymous nature, lack of consumer protections, and generally instability and susceptibility to scams. 

It's in a vendor's _and_ client's bests interest to cultivate the highest possible feedback scores. 

```{r}
nrow(cannabis)
```

Within the Cannabis subset there are 404,080 listings over 18 months. What are the relative percentages of feedback to this? 

```{r}

options(scipen = 999)

cannabis %>%
  group_by(fb) %>%
  summarise(n = n()) %>%
  mutate(freq = n/sum(n))

```

41% of listings are of unknown quality; they have no feedback. 56% of listings have the strongest possible feedback. It might be worthwhile to group feedback into a further generalization, from the consumer perspective:

- 2 and below: don't smoke this
- 3 and -1: roll the dice
- 4 and 5: go ahead and smoke it

An initial logistic regression looking at the how fb/feedback might be determined by price and number of words in the feedback listing.

```{r}
library(broom)

model01 <- glm(fb ~ price + f.words, family = binomial, data = cannabis)
tidy(model01)

```

```{r}
summary(model01)
```


```{r}

model02 <- glm(fb ~ usd + gold.oz + Index + Kind + Mids + Schwag + brent.oil + wti.oil + p.words, family = "binomial", data = cannabis)
tidy(model02)

```

```{r}
summary(model02)
```

```{r}
m02_output <- tidy(model02)
summary(m02_output)
exp(m02_output$estimate)
```

```{r}
m02.out <- coef(summary(model02))
m02.out[, "Estimate"] <- exp(coef(model02))
m02.out
```

```{r}
augment(model02)
```


